Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
Respond to reviewer 2 with more clarification on what Docker is

The fourth level includes packaging the analysis as a software package, *e.g.*, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as @Khaliq2020 have done.
Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]].
@Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

>>>>

The fourth level includes packaging the full analysis in a containerized software application, *e.g.*, Docker.
Docker is an open source containerization platform that enables users to package several applications and an operating system into containers, thereby standardising the executable components by combining application source code (or analyses) with the operating system required to run that analysis on any computer.
Using an open source language like R, Julia or Python allows us to share our work in a fashion where we know that the analysis will run exactly the same on every computer.
As an example of this approach, @Khaliq2020 provided a research compendium as a Docker container with a DOI and a full R package that enables readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]].
@Kamvar2015 took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
